LUCID: Learning-Enabled Uncertainty-Aware Certification of Stochastic Dynamical Systems

### 2025-08-01 docs/paper/main.tex
feat: update linear results

To close this gap (see Table~\ref{tab:qualitative_comparison}), we introduce \lucid, the first verification engine for black-box stochastic dynamical systems with quantified guarantees.
At its core, \lucid learns \glspl{cbc} for unknown systems based solely on data, by constructing an uncertainty-aware estimator of the expected system behavior based on \glspl{cme}~\cite{muandet2017kernel}.
Crucially, the underlying learning framework establishes quantified safety probabilities with distributionally robust guarantees for arbitrary smooth dynamics, thus relaxing the need for restrictive structural assumptions common to related approaches.
For instance, \citet{schoen2024distributionally} learn \glspl{cbc} for systems with polynomial dynamics and \citet{chen2025distributionally} assume systems with known deterministic component.
\begin{table}
    \centering
    \begin{tabular}{ccccccc}
        \toprule
        \textbf{Tool}                                    & \multicolumn{6}{c}{\textbf{Supported Features}}                                                                                                                                                                  \\[.4em]
                                                         & \rotatebox{90}{Guarantees}                      & \rotatebox{90}{Data Driven} & \rotatebox{90}{Stochastic Dyn.}  & \rotatebox{90}{Non-Poly. Dyn.} & \rotatebox{90}{Stat. Correct.} & \rotatebox{90}{Closed Loop} \\
        \midrule
        \textbf{\lucid}                                  & \cmark                                          & \cmark                      & \cmark                           & \cmark                         & \cmark                         & \cmark                      \\
        \trust~\shortcite{gardner2025trust}              & \cmark                                          & \cmark                      & \xmarkred                        & \xmarkred                      & \cmark\footnotemark[1]         & \cmark                      \\
        \fossil~\shortcite{edwards2024fossil}            & \cmark                                          & \xmarkred                   & \xmarkred                        & \cmark                         & NA                             & \cmark                      \\
        \omnisafe~\shortcite{ji2024omnisafe}             & \xmarkred                                       & \cmark                      & \cmark                           & \cmark                         & \xmarkred                      & \cmark                      \\
        \npinterval~\shortcite{harapanahalli2023forward} & \cmark                                          & \xmarkred                   & \cmark/\xmarkred\footnotemark[2] & \cmark                         & NA                             & \cmark                      \\
        % \deepsplit~\shortcite{henriksen2021deepsplit} & \xmarkred & \xmarkred & \cmark & \xmarkred& \xmarkred \\
        % \reluplex~\shortcite{katz2017reluplex} & \xmarkred & \xmarkred & \cmark & \xmarkred & \xmarkred \\
        % tool6                                            &                                                 &                             &                               &                                                                                             \\
        \bottomrule
    \end{tabular}
    \caption{Qualitative comparison with existing tools based on their supported features: quantified safety guarantees, data driven, stochastic dynamics, non-polynomial dynamics, statistical correctness guarantees of the learned model (only applicable if data driven), and support for closed-loop systems.}
    \label{tab:qualitative_comparison}
\end{table}
\footnotetext[1]{Assuming the data satisfies persistence of excitation.} % TRUST
\footnotetext[2]{Accepts non-deterministic bounded disturbances.} % npinterval

@@

We summarize the main contributions of this work:
\begin{itemize}
    \item We introduce \lucid, a novel verification engine that learns control barrier certificates from data using kernel-based \glspl{cme}. \lucid uses a tractable reformulation of the verification problem via a finite Fourier expansion, enabling efficient barrier synthesis based on a linear program.
    \item A robust and extensible software implementation, with both C++ and Python interfaces, supporting configuration via YAML, JSON, or Python scripts, and offering both a \gls{cli} and a \gls{gui}.
    \item Numerical evaluation on a suite of benchmarks, demonstrating \lucid{}’s unique capabilities, robustness, and practical utility.
\end{itemize}

@@

Although there exist model-\emph{based} efficient solutions to this problem for linear and control affine systems, especially for complex systems this is generally a semi-infinite problem, demanding a data-driven solution. Furthermore, for the data-driven case, establishing constraint (c) rigorously without relying on impractical assumptions is extremely challenging.

@@

\paragraph{Configuration}
% The system and the specification \lucid will check against shall be provided as a configuration to the program.
To certify safety of a system, \lucid accepts a configuration comprising data from the system and the safety specification.
We suggest defining it as a \yaml or equivalent \json file.%
\footnote[4]{The Json schema for \yaml and \json files can be found at \url{https://lucidtoolsource.gitlab.io/lucid/configuration_schema.json}}
% \OS{I would personally avoid the word "scenario", as it could be misunderstood with an actual run of the system.}
If more flexibility is needed, a Python script generating a configuration can be used instead,
with the only requirement being that it must contain a function named \lstinline|scenario_config| returning a \texttt{Configuration} object.
Regardless of their format, configuration files can be loaded with the command \lstinline|pylucid <config file>| to start the tool's verification pipeline.
The same configuration values can also be given directly as command line arguments.
\pylucid also provides a browser-based \gls{gui} to aid in the configuration and execution of the tool.
\Sadegh{space needs fixing before ".. to start ...".}

@@

\paragraph{Dataset}
% \todo{Should this be considered a component? It is more about the data loader} \Sadegh{This is good to have as a separate component.}
Due to its data-driven nature, all that \lucid needs to operate, is a set of sampled transitions $\data_N$ from the system, as shown in \eqref{eq:data}, and the safety specification itself.
% Data can be obtained by defining a function that takes as input the current state and control input and returns the next state, adding i.i.d. noise sampled from an appropriate distribution, or it may be collected from an external simulator or real-world system.
The samples can be specified directly in the configuration file, divided into $x^1,\ldots,x^N$ and $x^1_+,\ldots,x^N_+$:
\begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
x_samples: [[5.930e-01], ..., [-1.937e-01]]
xp_samples: [[3.015e-01], ..., [-1.018e-01]]
\end{lstlisting}
Alternatively, the samples can either be generated programmatically in the user-provided Python configuration script, or be stored in a separate file.
% Refer to the documentation for more details.
\begin{comment}
\begin{lstlisting}[language=iPython]
    def scenario_config():
    # ...
    # Sampling
    f = lambda x: x / 2
    c.x_samples = c.X_bounds.sample(1000)
    c.xp_samples = f(c.x_samples) + np.random.normal(scale=0.01)
    # ...
    return c
\end{lstlisting}
\end{comment}

@@

\paragraph{\Circled{3}~Tuner}
Being parameter-free approaches, kernel methods do not require the expensive learning processes of other machine learning methods, such as neural networks.
However, they still depend on a number of \hp, such as the kernel bandwidth $\sigma_f$, the lengthscale $\sigma_l$, and the regularization constant $\lambda$ (see \eqref{eq:gaussian_kernel}--\eqref{eq:empiricalEstimate}).
Changes in their values can have a significant impact on the \estimator's efficiency and accuracy.
The process of finding good values for these \hp is known as \emph{hyperparameter tuning}, with the optimal parameters being problem dependent.
\lucid provides a set of utilities, which specialize the \texttt{Tuner} interface, to aid in this task:
\begin{itemize}
    \item \texttt{MedianHeuristicTuner} uses the \emph{median heuristic} \cite{garreau2018largesampleanalysismedian} to produce rule-of-thumb-type estimates for the hyperparameters $\sigma_f$ and $\sigma_l$ of, e.g., the Gaussian kernel \eqref{eq:gaussian_kernel}, via closed-form expressions.
          This can offer a cheap starting point for successive fine-tuning.
    \item \texttt{LbfgsTuner} finds the \hp that maximize the \emph{log marginal likelihood}~\cite{rasmussen2006gaussian}, defined as
          \begin{equation*}
              \begin{split}
                   & \log p(X^+_N | X_N,\theta) =  - \frac{1}{2}X^+_N{}\T (K_{X}^N + N\lambda I_N)^{-1} X^+_N \\
                   & \hspace{40pt} -\frac{1}{2}\log |K_{X}^N + N\lambda I_N| - \frac{N}{2}\log(2\pi),
              \end{split}
          \end{equation*}
          where $\theta:=(\sigma_f,\sigma_l,\lambda)$ is the hyperparameter being optimized.
          The \texttt{LbfgsTuner} uses the L-BFGS or L-BFGS-B quasi-Newton optimization algorithms~\cite{book:nonlinear-programming},
          implemented in the \texttt{LBFGS++} library.\footnote{https://github.com/yixuan/LBFGSpp}
    \item \texttt{GridSearchTuner} implements the grid search method, exploring the space of possible \hp values to find the one that maximizes the \estimator's $R^2$ score, defined as $$R^2 = 1 - (\sum_{i=1}^M (y_i - \hat{y}_i)^2/\sum_{i=1}^M (y_i - \bar{y})^2).$$
\end{itemize}
Tuners open a wide range of possibilities to the user.
We recommend using them within a Python script generating a configuration to automate the tuning process before finalizing the \estimator's hyperparameter values:
\begin{lstlisting}[language=iPython,style=nonumbers]
def scenario_config(c: Configuration):
    ...
    t = LbfgsTuner(lb=[1e-5], ub=[1e5])
    c.estimator = KernelRidgeRegressor(
        kernel=GaussianKernel(),
    )
    c.estimator.fit(c.x_samples, c.xp_samples, tuner=t)
    return c
\end{lstlisting}
For the running example, we set the hyperparameters explicitly:
\begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
sigma_f: 15
sigma_l: [1.76]
lambda: 1.0e-5
\end{lstlisting}

@@

\paragraph{Running the Tool}
We have configured all the components needed to run \lucid.
Putting it all together in a single configuration file \texttt{config.yaml} we can run the tool with the command \lstinline|pylucid config.yaml --plot|.
\lucid will parse the configuration, synthesize a barrier certificate and plot the result.
For the running example, we obtain the barrier certificate shown in Figure~\ref{fig:example} for a time horizon of $T = 15$ certifying safety of the system in \eqref{eq:linear-system} with a probability of at least $93.73\%$ ($\eta = 0.013, \gamma=1.0, c = 0.003$). %\|B\| = 1.72

\begin{figure}
    \centering
    \begin{adjustbox}{max width=\columnwidth}
        \input{figures/example.pgf}
    \end{adjustbox}
    %\resizebox{\columnwidth}{!}{\import{figures}{example.pgf}}
    \caption{Barrier certificate for the running example.
        The state space $\X$ is plotted in the X axis, while the value of the barrier $\B$ is plotted in the Y axis.
        The green line represents the barrier value at time $t$.
        The initial and unsafe sets are highlighted in blue and red respectively. % \Sadegh{Figure not very readable.}
        }
    \label{fig:example}
\end{figure}

@@

To ascertain the performance of \lucid, we conduct a series of experiments, run on a Windows 10 machine with an AMD Ryzen 9 5950X 16-Core Processor @ 3.40 GHz, NVIDIA GeForce RTX 3090 GPU, and 64 GB of RAM.
All runs had the random seed set to $42$ to ensure reproducibility.

@@

Table~\ref{tbl:benchmarks_results} summarizes the results of all the experiments presented.
More details about the configurations and \hp used can be found in the Appendix.

\begin{figure}[ht]
    \begin{adjustbox}{clip,trim=0cm 1.7cm 0cm 2cm,max width=\columnwidth}
        \input{figures/barrier2.pgf}
    \end{adjustbox}
    %\includegraphics[trim={5cm 3cm 2cm 4cm},clip,width=\linewidth]{barrier2.pgf}
    \caption{\gls{cbc} synthesised for the \barrII benchmark.}
    \label{fig:CSBarr2}
\end{figure}

\begin{figure}[ht]
    \begin{adjustbox}{clip,trim=0cm 2cm 0cm 2cm,max width=\columnwidth}
        \input{figures/barrier3.pgf}
    \end{adjustbox}
    %\resizebox{\columnwidth}{!}{\import{figures}{barrier3.pgf}}%
    \caption{\gls{cbc} synthesised for the \barrIII benchmark.}
    \label{fig:CSBarr3}
\end{figure}

\begin{table}[tb]
    \centering
    \begin{tabular}{cccccc}
        \toprule
                    & \textbf{T} & \textbf{Freq} & \textbf{Lattice} & \textbf{Runtime} & \textbf{Safety} \\
                    &            &               & \textbf{Size}    & [mm:ss]          & \textbf{Prob}   \\ % Units
        \midrule
        \linear     & 15         & 5             & $704$            & 00:02            & 93.74\%         \\
        \barrII     & 5          & 15            & $350^2$          & 10:01            & 56.87\%         \\
        \barrIII    & 5          & 15            & $800^2$          & 64:20            & 42.25\%         \\
        \overtaking & 5          & 5             & $99^3$           & 46:33            & 30.32\%         \\
        \bottomrule
    \end{tabular}
    \caption{Computational benchmarks.
        The lattice size indicates the number of points of the lattice as the resolution for each dimension raised to the number of dimensions.
        $T$ is the number of time steps associated with the lower bound on the safety probability, displayed in the last column.
    }
    \label{tbl:benchmarks_results}
\end{table}

>>>>

To close this gap (see Table~\ref{tab:qualitative_comparison}), we introduce \lucid, the first verification engine for black-box stochastic dynamical systems with quantified guarantees.
At its core, \lucid learns \glspl{cbc} for unknown systems based solely on data, by constructing an uncertainty-aware estimator of the expected system behavior based on \glspl{cme}~\cite{muandet2017kernel}.
Crucially, the underlying learning framework establishes quantified safety probabilities with distributionally robust guarantees for arbitrary smooth dynamics, thus relaxing the need for restrictive structural assumptions common to related approaches.
For instance, \citet{schoen2024distributionally} learn \glspl{cbc} for systems with polynomial dynamics and \citet{chen2025distributionally} assume systems with known deterministic component.
\begin{table}
    \centering
    \begin{tabular}{ccccccc}
        \toprule
        \textbf{Tool}                                    & \multicolumn{6}{c}{\textbf{Supported Features}}                                                                                                                                                                  \\[.4em]
                                                         & \rotatebox{90}{Guarantees}                      & \rotatebox{90}{Data Driven} & \rotatebox{90}{Stochastic Dyn.}  & \rotatebox{90}{Non-Poly. Dyn.} & \rotatebox{90}{Stat. Correct.} & \rotatebox{90}{Closed Loop} \\
        \midrule
        \textbf{\lucid} (this work)                      & \cmark                                          & \cmark                      & \cmark                           & \cmark                         & \cmark                         & \cmark                      \\
        \trust~\shortcite{gardner2025trust}              & \cmark                                          & \cmark                      & \xmarkred                        & \xmarkred                      & \cmark\footnotemark[1]         & \cmark                      \\
        \fossil~\shortcite{edwards2024fossil}            & \cmark                                          & \xmarkred                   & \xmarkred                        & \cmark                         & NA                             & \cmark                      \\
        \omnisafe~\shortcite{ji2024omnisafe}             & \xmarkred                                       & \cmark                      & \cmark                           & \cmark                         & \xmarkred                      & \cmark                      \\
        \npinterval~\shortcite{harapanahalli2023forward} & \cmark                                          & \xmarkred                   & \cmark/\xmarkred\footnotemark[2] & \cmark                         & NA                             & \cmark                      \\
        % \deepsplit~\shortcite{henriksen2021deepsplit} & \xmarkred & \xmarkred & \cmark & \xmarkred& \xmarkred \\
        % \reluplex~\shortcite{katz2017reluplex} & \xmarkred & \xmarkred & \cmark & \xmarkred & \xmarkred \\
        % tool6                                            &                                                 &                             &                               &                                                                                             \\
        \bottomrule
    \end{tabular}
    \caption{Qualitative comparison with existing tools based on their supported features: quantified safety guarantees, data driven, stochastic dynamics, non-polynomial dynamics, statistical correctness guarantees of the learned model (only applicable if data driven), and support for closed-loop systems.}
    \label{tab:qualitative_comparison}
\end{table}
\footnotetext[1]{Assuming the data satisfies persistence of excitation.} % TRUST
\footnotetext[2]{Accepts non-deterministic bounded disturbances.} % npinterval

@@

We summarize the main contributions of this work:
\begin{itemize}
    \item We introduce \lucid, a novel verification engine that learns control barrier certificates from data using kernel-based \glspl{cme}. \lucid uses a tractable reformulation of the problem via a finite Fourier expansion, enabling efficient barrier synthesis based on a linear program.
    \item A robust and extensible software implementation, with both C++ and Python interfaces, supporting configuration via YAML, JSON, or Python scripts, and offering both a \gls{cli} and a \gls{gui}.
    \item Numerical evaluation on a suite of benchmarks, demonstrating \lucid{}’s unique capabilities, robustness, and practical utility.
\end{itemize}

@@

Although there exist model-\emph{based} efficient solutions to this problem for linear and control affine systems, this is generally a semi-infinite problem, demanding a data-driven solution. Furthermore, for the data-driven case, establishing constraint (c) rigorously without relying on impractical assumptions is extremely challenging.

@@

\paragraph{Configuration}
% The system and the specification \lucid will check against shall be provided as a configuration to the program.
To certify safety of a system, \lucid accepts a configuration comprising data from the system and the safety specification.
We suggest defining it as a \yaml or equivalent \json file.%
%\footnote[4]{The Json schema for \yaml and \json files can be found at \url{https://lucidtoolsource.gitlab.io/lucid/configuration_schema.json}}
% \OS{I would personally avoid the word "scenario", as it could be misunderstood with an actual run of the system.}
If more flexibility is needed, a Python script generating a configuration can be used instead,
with the only requirement being that it must contain a function named \lstinline|scenario_config| returning a \texttt{Configuration} object.
Regardless of their format, configuration files can be loaded with the command \lstinline|pylucid <config file>| to start the tool's verification pipeline.
The same configuration values can also be given directly as command line arguments.
\pylucid also provides a browser-based \gls{gui} to aid in the configuration and execution of the tool.
\Sadegh{space needs fixing before ".. to start ...".}

@@

\paragraph{Dataset}
% \todo{Should this be considered a component? It is more about the data loader} \Sadegh{This is good to have as a separate component.}
Due to its data-driven nature, all that \lucid needs to operate, is a set of sampled transitions $\data_N$ from the system, as shown in \eqref{eq:data}, and the safety specification itself.
% Data can be obtained by defining a function that takes as input the current state and control input and returns the next state, adding i.i.d. noise sampled from an appropriate distribution, or it may be collected from an external simulator or real-world system.
The samples can be specified directly in the configuration file, divided into $x^1,\ldots,x^N$ and $x^1_+,\ldots,x^N_+$:
\begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
x_samples: [[5.930e-01], ..., [-1.937e-01]]
xp_samples: [[3.015e-01], ..., [-1.018e-01]]
\end{lstlisting}
Alternatively, the samples can either be generated by the Python configuration script, or be stored in a separate file.
% Refer to the documentation for more details.
\begin{comment}
\begin{lstlisting}[language=iPython]
    def scenario_config():
    # ...
    # Sampling
    f = lambda x: x / 2
    c.x_samples = c.X_bounds.sample(1000)
    c.xp_samples = f(c.x_samples) + np.random.normal(scale=0.01)
    # ...
    return c
\end{lstlisting}
\end{comment}

@@

\paragraph{\Circled{3}~Tuner}
Being parameter-free approaches, kernel methods do not require the expensive learning processes of other machine learning methods, such as neural networks.
However, they still depend on a number of \hp, such as the kernel bandwidth $\sigma_f$, the lengthscale $\sigma_l$, and the regularization constant $\lambda$ (see \eqref{eq:gaussian_kernel}--\eqref{eq:empiricalEstimate}).
Changes in their values can have a significant impact on the \estimator's efficiency and accuracy.
The process of finding good values for these \hp is known as \emph{hyperparameter tuning}, with the optimal parameters being problem dependent.
\lucid provides a set of utilities, which specialize the \texttt{Tuner} interface, to aid in this task:
\begin{itemize}
    \item \texttt{MedianHeuristicTuner} uses the \emph{median heuristic} \cite{garreau2018largesampleanalysismedian} to produce rule-of-thumb-type estimates for the \hp $\sigma_f$ and $\sigma_l$ of, e.g., the Gaussian kernel \eqref{eq:gaussian_kernel}, via closed-form expressions.
          It can be useful as a starting point for subsequent improvements.
    \item \texttt{LbfgsTuner} finds the \hp that maximize the \emph{log marginal likelihood}~\cite{rasmussen2006gaussian}, defined as
          \begin{equation*}
              \begin{split}
                   & \log p(X^+_N | X_N,\theta) =  - \frac{1}{2}X^+_N{}\T (K_{X}^N + N\lambda I_N)^{-1} X^+_N \\
                   & \hspace{40pt} -\frac{1}{2}\log |K_{X}^N + N\lambda I_N| - \frac{N}{2}\log(2\pi),
              \end{split}
          \end{equation*}
          where $\theta:=(\sigma_f,\sigma_l,\lambda)$ is the hyperparameter being optimized.
          We use the L-BFGS or L-BFGS-B quasi-Newton optimization algorithms~\cite{book:nonlinear-programming},
          implemented in the \texttt{LBFGS++} library~\cite{LBFGSpp}.
          %          \footnote{https://github.com/yixuan/LBFGSpp}
    \item \texttt{GridSearchTuner} implements the grid search method, exploring the space of possible \hp values to find the one that maximizes the \estimator's $R^2$ score, defined as $$R^2 = 1 - (\sum_{i=1}^M (y_i - \hat{y}_i)^2/\sum_{i=1}^M (y_i - \bar{y})^2).$$
\end{itemize}
Tuners open a wide range of possibilities to the user.
We recommend using them within a Python script generating a configuration to automate the tuning process before finalizing the \estimator's hyperparameter values:
\begin{lstlisting}[language=iPython,style=nonumbers]
def scenario_config(c: Configuration):
    t = LbfgsTuner(lb=[1e-5], ub=[1e5])
    c.estimator = KernelRidgeRegressor()
    c.estimator.fit(c.x_samples, c.xp_samples, tuner=t)
    return c
\end{lstlisting}
In this example, we set the \hp explicitly:
\begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
sigma_f: 15
sigma_l: [1.2]
lambda: 1.0e-5
\end{lstlisting}

@@

\paragraph{Running the Tool}
We have configured all the components needed to run \lucid.
Putting it all together in a single configuration file \texttt{config.yaml} we can run the tool with the command \lstinline|pylucid config.yaml --plot|.
\lucid will parse the configuration, synthesize a barrier certificate and plot the result.
For the running example, we obtain the barrier certificate shown in Figure~\ref{fig:example} for a time horizon of $T = 15$ certifying safety of the system in \eqref{eq:linear-system} with a probability of at least $95.12\%$ ($\eta = 0.03, \gamma=1.0, c = 0.001$). %\|B\| = 1.72

\begin{figure}
    \centering
    \begin{adjustbox}{max width=\columnwidth}
        \input{figures/example.pgf}
    \end{adjustbox}
    %\resizebox{\columnwidth}{!}{\import{figures}{example.pgf}}
    \caption{Barrier certificate for the example.
        The value of the barrier $\B$ is plotted against the state space $\X$.
        The green line represents the barrier value.
        The initial and unsafe sets are highlighted in blue and red respectively. % \Sadegh{Figure not very readable.}
    }
    \label{fig:example}
\end{figure}

@@

To ascertain the performance of \lucid, we conduct a series of experiments on a Windows 10 machine with an AMD Ryzen 9 5950X 16-Core Processor @ 3.40 GHz, NVIDIA GeForce RTX 3090 GPU, and 64 GB of RAM.
All runs had the random seed set to $42$ to ensure reproducibility.

@@

Table~\ref{tbl:benchmarks_results} summarizes the results of all the experiments presented.
More details about the dynamics, configurations and \hp used can be found in the Appendix.

\begin{figure}[ht]
    \begin{adjustbox}{clip,trim=0cm 1.7cm 0cm 2cm,max width=\columnwidth}
        \input{figures/barrier2.pgf}
    \end{adjustbox}
    %\includegraphics[trim={5cm 3cm 2cm 4cm},clip,width=\linewidth]{barrier2.pgf}
    \caption{\gls{cbc} synthesized for the \barrII benchmark.}
    \label{fig:CSBarr2}
\end{figure}

\begin{figure}[ht]
    \begin{adjustbox}{clip,trim=0cm 2cm 0cm 2cm,max width=\columnwidth}
        \input{figures/barrier3.pgf}
    \end{adjustbox}
    %\resizebox{\columnwidth}{!}{\import{figures}{barrier3.pgf}}%
    \caption{\gls{cbc} synthesized for the \barrIII benchmark.}
    \label{fig:CSBarr3}
\end{figure}

\begin{table}[tb]
    \centering
    \begin{tabular}{cccccc}
        \toprule
                    & \textbf{T} & \textbf{Freq.} & \textbf{Lattice} & \textbf{Runtime} & \textbf{Safety} \\
                    &            &                & \textbf{Size}    & [mm:ss]          & \textbf{Prob.}  \\ % Units
        \midrule
        \linear     & 15         & 5              & $704$            & 00:02            & 95.12\%         \\
        \barrII     & 5          & 15             & $350^2$          & 10:01            & 56.87\%         \\
        \barrIII    & 5          & 15             & $800^2$          & 64:20            & 42.25\%         \\
        \overtaking & 5          & 5              & $99^3$           & 46:33            & 30.32\%         \\
        \bottomrule
    \end{tabular}
    \caption{Computational benchmarks.
        The lattice size indicates the number of points of the lattice as the resolution for each dimension raised to the number of dimensions.
        $T$ is the time horizon associated with the lower bound on the safety probability, displayed in the last column.
    }
    \label{tbl:benchmarks_results}
\end{table}
